### 2015-09-17 stuff/dirfields/DirFields.tex
...

\documentclass{scrartcl}

@@

@@

%surface (manifold) -> M, S, \Omega 
\newcommand{\M}{M}
%volume element (volume measure) -> \mu, dA, d\Omega
\newcommand{\dA}{dA}
%director field (contra-vector)
\newcommand{\p}{\mathbf{p}}
\newcommand{\q}{\mathbf{q}}
%director field (co-vector, flat of contra-vector)
\newcommand{\pfl}{\mathbf{p}^{\flat}}
\newcommand{\qfl}{\mathbf{q}^{\flat}}
%discrete director field (co-vector, flat of contra-vector)
\newcommand{\pflh}{\mathbf{p}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\ph}{\mathbf{p}_{h}}
%discrete PD director field (co-vector, flat of contra-vector)
\newcommand{\PDpflh}{\underline{\mathbf{p}}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\PDph}{\underline{\mathbf{p}}_{h}}
%Frank Oseen Energy (without Lagrange term for normalizing)
\newcommand{\EOS}{E_{\text{OS}}}
%Normalizing energy
\newcommand{\EN}{E_{n}}
%Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LB}{\Delta^{\text{\tiny RR}}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCB}{\Delta^{\text{\tiny GD}}}
%Laplace-deRham
\newcommand{\LDR}{\Delta^{\text{\tiny dR}}}
%discrete Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LBh}{\LB_{h}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCBh}{\LCB_{h}}
%Laplace-deRham
\newcommand{\LDRh}{\LDR_{h}}
%Landau symbol
\renewcommand{\O}{\mathcal{O}}
%Vertices
\newcommand{\V}{\mathcal{V}}
%Edges
\newcommand{\E}{\mathcal{E}}
%Faces
\newcommand{\F}{\mathcal{F}}
%edge vector
\newcommand{\e}{\mathbf{e}}
%vertex vector
\renewcommand{\v}{\mathbf{v}}

@@

\section{Model equations}
  To minimize the energy \( E := \EOS + \EN \) we choose a time evolving approach. 
  Hence, with the fundamental lemma of calculus of variations, we will use the time depended differential equation in terms of exterior
  calculus
  \begin{align}
    \partial_{t}\pfl = -\frac{\delta E}{\delta\pfl}
                     = -K_{0}\LDR\pfl - K_{n} \left( \left\| \pfl \right\|^{2} - 1 \right)\pfl
  \end{align}
  or in general, if we don't want to use the One-Constant-Approximation,
  \begin{align}
    \partial_{t}\pfl = \left( K_{1}\LCB + K_{3}\LB\right)\pfl - K_{n} \left( \left\| \pfl \right\|^{2} - 1 \right)\pfl
  \end{align}
  Note that if we apply the Hodge operator on the whole equations, we get the Hodge dual equations
  \begin{align}
    \partial_{t}(*\pfl) &= -K_{0}\LDR (*\pfl) - K_{n} \left( \left\| \pfl \right\|^{2} - 1 \right)(*\pfl) \\
                        &=  \left( K_{1}\LB + K_{3}\LCB\right) (*\pfl) - K_{n} \left( \left\| \pfl \right\|^{2} - 1 \right)(*\pfl)
  \end{align}
  which are very useful for the DEC discretization later in context.
  But this leads to pay attention, because only in the first line (One-Constant-Approximation) we see, 
  that the Hodge dual equations in \( *\pfl \) is the same as the primal equation in \( \pfl \). 
  In the general case (second line), we must "swap" the Laplace operators.

\section{A DEC approach}

@@

  The main concept to represent a discrete 1-form \( \pflh\in\Lambda_{h}(K) \) is to approximate the contraction of the continuous 1-Form 
  \( \pfl\in\Lambda(M) \) on all edges \( e\in\E \)
  \begin{align}
    \pflh(e) := \int_{\pi(e)}\pfl \approx \int_{0}^{1} \pfl_{X_{e}(\tau)}\left( \dot{X}_{e}(t) \right) dt = \pfl_{X_{e}(\tau)}(\e)
  \end{align}
  where \( \pi:K\rightarrow \M \) is the glueing map, who project the elements of the surface mesh to the manifold.
  \( X_{e}(t) = t\v_{2} + (1-t)\v_{1} \) is the linear barycentric parametrisation of the edge \( e=\left[ v_{1}, v_{2} \right]\).
  The existence of a intermediate value \( \tau\in\left[ 0,1 \right] \), so that \( \e\in T_{X_{e}(\tau)}M \),
  is ensured by the mean value theorem.
  Other discrete forms of arbitrary degree and theirs hodge duals can be interpreted in a similarly way.

@@

    Approximating the norm \( \left\| \pfl \right\| \) on a edge \( e\in\E \) is not so easy like the development of discrete linear
    operators. 
    We only know how \( \pflh \) "act" on a single edge, so \( \pflh \) gives us only one dimensional informations.
    In other words, we only know the proportion \( \ph \cdot \e = \pflh (e)\) of the discrete contra vector field \( \ph = \left( \pflh \right)^{\sharp} \) in the
    \( \e \) direction, but we don't know the length of \( \ph \) defined on this edge.

    ...some averaging techniques and why these sucks...

    One way out is to rise the dimension of the discrete 1-forms, therefor we introduce some bases at the intersection 
    \( c(e) = e\cap (\star e) \) of a edge and its dual edge to describe discrete contra- and covariant vector fields in a local (flat)
    coordinate system.

    The basis for contravariant vectors at \( c(e) \) is composed of
    \begin{align}
      \partial_{e}X &:= \e = \v_{2} - \v_{1} \\
      \partial_{\star e}X &:= *\e =  c(f_{2}) - c(f_{1})
    \end{align}
    if \( e=\left[ v_{1}, v_{2} \right] \) and the face \( f_{1} \) lay right and \( f_{2} \) left of \( e \) (...figure...). 
    This definitions are consistent with the canonical basis, if the position \( X \) is a barycentric parametrisation of the edge \( e \)
    resp. its dual, i.e. for
    \begin{align}
      X_{e}(t_{e}) &= t_{e}\v_{2} + \left( 1 - t_{e} \right)\v_{2} \text{ for } t\in[0,1]\\
      X_{\star e}(t_{\star e}) &=\begin{cases}
                        2t_{\star e}c(e) + \left( 1 - 2t_{\star e} \right) c(f_{1}) & \text{if } t_{\star e}\in\left[ 0 , \frac{1}{2} \right] \\
                        \left(1 - t_{\star e}\right) c(e) + \left( 2t_{\star e} - 1 \right) c(f_{1}) 
                                & \text{if } t_{\star e}\in \left[\frac{1}{2} , 1\right]
                      \end{cases}
    \end{align}
    holds \( \partial_{e}X = \partial_{t_{e}}X_{e} \) 
    and \( \partial_{\star e}X = \frac{1}{2} \left( \partial_{t_{\star e}}X_{\star e}|_{\left[ 0 , \frac{1}{2} \right]} 
                                                   + \partial_{t_{\star e}}X_{\star e}|_{\left[\frac{1}{2}, 1 \right]}\right) \).
    Therefore we get the local metric tensor
    \begin{align}
      g_h(e) &= \left| e \right|^{2} \left( dx^{e} \right)^{2} + \left| \star e \right|^{2} \left( dx^{\star e} \right)^{2}
    \end{align}
    where \( \left\{  dx^{e}, dx^{\star e} \right\} \) are the dual base of \( \left\{ \partial_{e}X, \partial_{\star e}X \right\} \),
    i.e. \( dx^{i}\left(\partial_{j}X\right) = \delta^{i}_{j} \) for \( i,j\in\left\{ e, \star e \right\} \).
    This gives us the great possibility to define
    \begin{align}
      \PDpflh(e) &:= \pflh(e)dx^{e} + \pflh(\star e)  dx^{\star e} \\
                   &= \pflh(e)dx^{e} - \frac{\left| \star e \right|}{\left| e \right|} \left(*\pflh\right)(e)  dx^{\star e} \\
      \PDph(e) &:= \left(\PDpflh(e)\right)^{\sharp} 
                 = \frac{1}{\left| e \right|^{2}} \pflh(e)\partial_{e}X + \frac{1}{\left|\star e \right|^{2}} \pflh(\star e)\partial_{\star e}X \\
               & =  \frac{1}{\left| e \right|} \left( \frac{1}{\left| e \right|} \pflh(e)\partial_{e}X 
                                                     -\frac{1}{\left|\star e \right|} \left(*\pflh\right)(e) \partial_{\star e}X\right)
    \end{align}
    We call \( \PDpflh(e) \) the discrete Primal-Dual-1-form (short PD-1-form) and \( \PDph \) the discrete Primal-Dual-vector field
    (short PD-vector field).
    Hence, we get for the square of the norm on \( c(e) \) by contract the PD-1-Form with its corresponding PD-Vector
    \begin{align}
      \left\| \PDpflh \right\|^{2}(e) := \left( \PDpflh\left( \PDph \right) \right)(e)
                                       = \frac{1}{\left| e \right|^{2}}\left( \left[ \pflh(e) \right]^{2} 
                                                                             +\left[ \left(*\pflh\right)(e) \right]^{2}\right)
    \end{align}

>>>>

\documentclass[a4paper,11pt]{scrartcl}

\usepackage[margin=2.cm]{geometry}

@@

\usepackage[pdftex]{graphicx}

@@

%surface (manifold) -> M, S, \Omega 
\newcommand{\M}{M}
%volume element (volume measure) -> \mu, dA, d\Omega
\newcommand{\dA}{dA}
%director field (contra-vector)
\newcommand{\p}{\mathbf{p}}
\newcommand{\q}{\mathbf{q}}
%director field (co-vector, flat of contra-vector)
\newcommand{\pfl}{\mathbf{p}^{\flat}}
\newcommand{\qfl}{\mathbf{q}^{\flat}}
%discrete director field (co-vector, flat of contra-vector)
\newcommand{\pflh}{\mathbf{p}^{\flat}_{h}}
\newcommand{\pflhOld}{\widehat{\mathbf{p}}^{\flat}_{h}}
\newcommand{\qflh}{\mathbf{q}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\ph}{\mathbf{p}_{h}}
%discrete PD director field (co-vector, flat of contra-vector)
\newcommand{\PDpflh}{\underline{\mathbf{p}}^{\flat}_{h}}
\newcommand{\PDqflh}{\underline{\mathbf{q}}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\PDph}{\underline{\mathbf{p}}_{h}}
%discrete PD director field OLD SOLUTION (co-vector, flat of contra-vector)
\newcommand{\PDpflhOld}{\underline{\widehat{\mathbf{p}}}^{\flat}_{h}}
%Frank Oseen Energy (without Lagrange term for normalizing)
\newcommand{\EOS}{E_{\text{OS}}}
%Normalizing energy
\newcommand{\EN}{E_{n}}
%Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LB}{\Delta^{\text{\tiny RR}}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCB}{\Delta^{\text{\tiny GD}}}
%Laplace-deRham
\newcommand{\LDR}{\Delta^{\text{\tiny dR}}}
%discrete Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LBh}{\LB_{h}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCBh}{\LCB_{h}}
%Laplace-deRham
\newcommand{\LDRh}{\LDR_{h}}
%Landau symbol
\renewcommand{\O}{\mathcal{O}}
%Vertices
\newcommand{\V}{\mathcal{V}}
%Edges
\newcommand{\E}{\mathcal{E}}
%Faces
\newcommand{\F}{\mathcal{F}}
%edge vector
\newcommand{\e}{\mathbf{e}}
%vertex vector
\renewcommand{\v}{\mathbf{v}}

@@

\section{Model equations}
  To minimize the energy \( E := \EOS + \EN \) we choose a time evolving approach. 
  Hence, with the fundamental lemma of calculus of variations, we will use the time depended differential equation in terms of exterior
  calculus
  \begin{align} \label{eqPOC}
    \partial_{t}\pfl = -\frac{\delta E}{\delta\pfl}
                     = -K_{0}\LDR\pfl - K_{n} \left( \left\| \pfl \right\|^{2} - 1 \right)\pfl
  \end{align}
  or in general, if we don't want to use the One-Constant-Approximation,
  \begin{align} \label{eqP}
    \partial_{t}\pfl = \left( K_{1}\LCB + K_{3}\LB\right)\pfl - K_{n} \left( \left\| \pfl \right\|^{2} - 1 \right)\pfl
  \end{align}
  Note that if we apply the Hodge operator on the whole equations, we get the Hodge dual equations
  \begin{align}
    \label{eqDOC}
    \partial_{t}(*\pfl) &= -K_{0}\LDR (*\pfl) - K_{n} \left( \left\| \pfl \right\|^{2} - 1 \right)(*\pfl) \\
    \label{eqD}
                        &=  \left( K_{1}\LB + K_{3}\LCB\right) (*\pfl) - K_{n} \left( \left\| \pfl \right\|^{2} - 1 \right)(*\pfl)
  \end{align}
  which are very useful for the DEC discretization later in context.
  But this leads to pay attention, because only in the first line (One-Constant-Approximation) we see, 
  that the Hodge dual equations in \( *\pfl \) is the same as the primal equation in \( \pfl \). 
  In the general case (second line), we must "swap" the Laplace operators.

\section{Needed DEC stuff}

@@

  The main concept to represent a discrete 1-form \( \pflh\in\Lambda_{h}^{1}(K) \) is to approximate the contraction of the continuous 1-Form 
  \( \pfl\in\Lambda^{1}(M) \) on all edges \( e\in\E \)
  \begin{align}
    \pflh(e) := \int_{\pi(e)}\pfl \approx \int_{0}^{1} \pfl_{X_{e}(\tau)}\left( \dot{X}_{e}(t) \right) dt = \pfl_{X_{e}(\tau)}(\e)
  \end{align}
  where \( \pi:K\rightarrow \M \) is the glueing map, who project the elements of the surface mesh to the manifold.
  \( X_{e}(t) = t\v_{2} + (1-t)\v_{1} \) is the linear barycentric parametrisation of the edge \( e=\left[ v_{1}, v_{2} \right]\).
  The existence of a intermediate value \( \tau\in\left[ 0,1 \right] \), so that \( \e\in T_{X_{e}(\tau)}M \),
  is ensured by the mean value theorem.
  Other discrete forms of arbitrary degree and theirs hodge duals can be interpreted in a similarly way.

@@

    Approximating the norm \( \left\| \pfl \right\| \) on a edge \( e\in\E \) is not so easy like the development of discrete linear
    operators. 
    We only know how \( \pflh \) "act" on a single edge, so \( \pflh \) gives us only one dimensional informations.
    In other words, we only know the proportion \( \ph \cdot \e = \pflh (e)\) of the discrete contravariant vector field 
    \( \ph = \left( \pflh \right)^{\sharp} \) in the
    \( \e \) direction, but we don't know the length of \( \ph \) defined on this edge.

    ...maybe some averaging techniques, which I tried and why these sucks...

    One way out is to rise the dimension of the discrete 1-forms, therefor we introduce some bases at the intersection 
    \( c(e) = e\cap (\star e) \) of a edge and its dual edge to describe discrete contra- and covariant vector fields in a local 
    (piecewise flat)
    coordinate system.

    The basis for contravariant vectors at \( c(e) \) is composed of
    \begin{align}
      \partial_{e}X &:= \e = \v_{2} - \v_{1} \\
      \partial_{\star e}X &:= *\e =  c(f_{2}) - c(f_{1})
    \end{align}
    if \( e=\left[ v_{1}, v_{2} \right] \) and the face \( f_{1} \) lay right and \( f_{2} \) left of \( e \) (...figure...). 
    This definitions are consistent with the canonical basis, if the position \( X \) is a barycentric parametrisation of the edge \( e \)
    resp. its dual, i.e. for
    \begin{align}
      X_{e}(t_{e}) &= t_{e}\v_{2} + \left( 1 - t_{e} \right)\v_{2} \text{ for } t\in[0,1]\\
      X_{\star e}(t_{\star e}) &=\begin{cases}
                        2t_{\star e}c(e) + \left( 1 - 2t_{\star e} \right) c(f_{1}) & \text{if } t_{\star e}\in\left[ 0 , \frac{1}{2} \right] \\
                        \left(1 - t_{\star e}\right) c(e) + \left( 2t_{\star e} - 1 \right) c(f_{1}) 
                                & \text{if } t_{\star e}\in \left[\frac{1}{2} , 1\right]
                      \end{cases}
    \end{align}
    holds \( \partial_{e}X = \partial_{t_{e}}X_{e} \) 
    and \( \partial_{\star e}X = \frac{1}{2} \left( \partial_{t_{\star e}}X_{\star e}|_{\left[ 0 , \frac{1}{2} \right]} 
                                                   + \partial_{t_{\star e}}X_{\star e}|_{\left[\frac{1}{2}, 1 \right]}\right) \).
    Therefore we get the local metric tensor
    \begin{align}
      \mathbf{g}_h(e) &= \left| e \right|^{2} \left( dx^{e} \right)^{2} + \left| \star e \right|^{2} \left( dx^{\star e} \right)^{2}
    \end{align}
    where \( \left\{  dx^{e}, dx^{\star e} \right\} \) are the dual base of \( \left\{ \partial_{e}X, \partial_{\star e}X \right\} \),
    i.e. \( dx^{i}\left(\partial_{j}X\right) = \delta^{i}_{j} \) for \( i,j\in\left\{ e, \star e \right\} \).
    This gives us the great possibility to define
    \begin{align}
      \PDpflh(e) &:= 
                   \begin{bmatrix}
                     \pflh \\ *\pflh 
                   \end{bmatrix}_{\text{PD}} (e)
                   := \pflh(e)dx^{e} + \pflh(\star e)  dx^{\star e} \\
                   &= \pflh(e)dx^{e} - \frac{\left| \star e \right|}{\left| e \right|} \left(*\pflh\right)(e)  dx^{\star e} \\
      \PDph(e) &:= \left(\PDpflh(e)\right)^{\sharp} 
                 = \frac{1}{\left| e \right|^{2}} \pflh(e)\partial_{e}X + \frac{1}{\left|\star e \right|^{2}} \pflh(\star e)\partial_{\star e}X \\
               & =  \frac{1}{\left| e \right|} \left( \frac{1}{\left| e \right|} \pflh(e)\partial_{e}X 
                                                     -\frac{1}{\left|\star e \right|} \left(*\pflh\right)(e) \partial_{\star e}X\right)
    \end{align}
    We call \( \PDpflh(e) \) the discrete Primal-Dual-1-form (short PD-1-form) and \( \PDph \) the discrete Primal-Dual-vector field
    (short PD-vector field).
    Hence, we get for the square of the norm on \( c(e) \) by contract the PD-1-Form with its corresponding PD-Vector
    \begin{align}
      \left\| \PDpflh \right\|_{h}^{2}(e) := \left( \PDpflh\left( \PDph \right) \right)(e)
                                       = \frac{1}{\left| e \right|^{2}}\left( \left[ \pflh(e) \right]^{2} 
                                                                             +\left[ \left(*\pflh\right)(e) \right]^{2}\right)
    \end{align}
    In general, we also get a local discrete inner product between \( \PDpflh \) and another PD-1-form \( \PDqflh \) by
    \begin{align}
      \left\langle \PDqflh , \PDpflh \right\rangle_{h}(e)
          &:= \left( \PDqflh\left( \PDph \right) \right)(e)
                                       = \frac{1}{\left| e \right|^{2}}\left( \left[\pflh\qflh\right](e) 
                                                                             +\left[\left(*\pflh\right)\left(*\qflh\right)\right](e) \right)
    \end{align}

\section{Discrete PD-Problem, a DEC approach}
  To use a PD-1-form solution, we must also determine the dual part \( *\pflh \), 
  therefore we discretize the Hodge dual equation \eqref{eqDOC} (resp. \eqref{eqD}) simultaneous to the primal equation
  \eqref{eqPOC} (resp. \eqref{eqP}).
  This leads to the DEC-discretized Primal-Dual-problem (DEC-PD-problem) 
  \begin{align}
    \left[ \partial_{t} + K_{0}\LDRh + K_{n}\left( \left\| \PDpflh \right\|_{h}^{2} - 1 \right) \right]\PDpflh &= 0
  \end{align}
  respective, without the One-Constant-Approximation,  
  \begin{align}
    \left[ \partial_{t} -   
            \begin{bmatrix}
               K_{1} \\ K_{3}
            \end{bmatrix} \LCBh
            -\begin{bmatrix}
               K_{3} \\ K_{1}
            \end{bmatrix} \LBh
    + K_{n}\left( \left\| \PDpflh \right\|_{h}^{2} - 1 \right) \right]\PDpflh &= 0
  \end{align}

  \subsection{Time discretization}
    The simplest way to discretize the DEC-PD-problem in time is to use a implicit Euler scheme, 
    where we handle the norm \( \left\| \PDpflh \right\|_{h}^{2} \) explicit.
    For one Euler step, we have to solve
    \begin{align}
      \left[ \frac{1}{\tau} + K_{0}\LDRh + K_{n}\left( \left\| \PDpflhOld \right\|_{h}^{2}(e) - 1 \right) \right]\PDpflh(e) 
          &= \frac{1}{\tau} \PDpflhOld(e)
    \end{align}
    resp.
    \begin{align}
       \left[  \frac{1}{\tau}-   
            \begin{bmatrix}
               K_{1} \\ K_{3}
            \end{bmatrix} \LCBh
            -\begin{bmatrix}
               K_{3} \\ K_{1}
            \end{bmatrix} \LBh
    + K_{n}\left( \left\| \PDpflhOld \right\|_{h}^{2}(e) - 1 \right) \right]\PDpflh(e) 
          &= \frac{1}{\tau} \PDpflhOld(e)
    \end{align}
    for all \( e\in\E \).
    \( \PDpflhOld  \) is the solution of the last time step or the initial condition, if this is the first Euler step.
    \( \tau = t - \hat{t}  \) is the time step wide.

    The drawback of this semi-implicit Euler scheme is, that we need very small \( \tau \).
    Therefore, it is better to use a Taylor-linearisation for  \( \left\| \PDpflh \right\|_{h}^{2}\PDpflh \).
    First we calculate the partially component derivative on a edge \( e\in\E \) of
    \begin{align}
        \Phi\left( \PDpflh \right) &= \Phi \left( \pflh, *\pflh \right)
              :=\left\| \PDpflh \right\|_{h}^{2}\PDpflh 
              = \frac{1}{\left| e \right|^{2}} \left( \left( \pflh \right)^{2} 
                                                  +\left( *\pflh \right)^{2} \right)
                                     \begin{bmatrix}
                                       \pflh \\ *\pflh
                                     \end{bmatrix}
    \end{align}
    (Henceforward, for a better readability, the arguments \( e \) are omitted).
    Hence, we obtain
    \begin{align}
      \partial_{\pflh}\Phi
          &= \frac{1}{\left| e \right|^{2}}
                \begin{bmatrix}
                  3\left( \pflh \right)^{2} + \left( *\pflh \right)^{2} \\
                  2\pflh\left( *\pflh \right)
                \end{bmatrix} \\
      \partial_{*\pflh}\Phi
          &= \frac{1}{\left| e \right|^{2}}
                \begin{bmatrix}
                  2\pflh\left( *\pflh \right) \\
                  \left( \pflh \right)^{2} + 3 \left( *\pflh \right)^{2} \\
                \end{bmatrix}
    \end{align}
    For one step Taylor at \( \PDpflhOld \), we get
    \begin{align}
      \Phi(\PDpflh) &\approx  \Phi(\PDpflhOld) + \left( \pflh - \pflhOld \right)\partial_{\pflh}\Phi\left( \PDpflhOld \right)
                          + \left( *\pflh - *\pflhOld \right)\partial_{*\pflh}\Phi\left( \PDpflhOld \right) \\
                    &= \left\| \PDpflhOld \right\|_{h}^{2}\PDpflhOld
                    +\frac{1}{\left| e \right|^{2}}
                      \begin{bmatrix}
                        \left( \pflh - \pflhOld \right)\left( 3\left( \pflh \right)^{2} + \left( *\pflh \right)^{2} \right)
                        + 2\left(*\pflh - *\pflhOld\right)\pflh\left( *\pflh \right) \\
                        2\left( \pflh - \pflhOld \right)\pflh\left( *\pflh \right)
                        +\left(*\pflh - *\pflhOld\right)\left( 3\left( \pflh \right)^{2} + \left( *\pflh \right)^{2} \right)
                      \end{bmatrix} \\
       &= \left\| \PDpflhOld \right\|_{h}^{2}\PDpflhOld
          \begin{aligned}[t]
            &-\frac{3}{\left| e \right|^{2}}\left( \left( \pflhOld \right)^{2} + \left( *\pflhOld \right)^{2} \right)\PDpflhOld
            +\frac{2}{\left| e \right|^{2}}
                    \begin{bmatrix}
                      \left( *\pflhOld \right)^{2} \\  \left( \pflhOld \right)^{2}
                    \end{bmatrix}
                    \PDpflhOld \\
            &+\frac{1}{\left| e \right|^{2}}\left( \left( \pflhOld \right)^{2} + \left( *\pflhOld \right)^{2} \right)\PDpflh
            +\frac{2}{\left| e \right|^{2}}
                    \begin{bmatrix}
                      \pflh\pflhOld \\ \left( *\pflh \right)\left( *\pflhOld \right)
                    \end{bmatrix}
                    \PDpflhOld \\
            &+\frac{2}{\left| e \right|^{2}}
                \begin{bmatrix}
                  \left(*\pflh - *\pflhOld\right)\left( *\pflh \right)\\
                  \left( \pflh - \pflhOld \right)\pflh
                \end{bmatrix}
                \PDpflhOld
          \end{aligned}\\
       &= -2\left\| \PDpflhOld \right\|_{h}^{2}\PDpflhOld 
            + \left\| \PDpflhOld \right\|_{h}^{2}\PDpflh
            + 2\left\langle \PDpflh, \PDpflhOld \right\rangle_{h}\PDpflhOld
    \end{align}
    The inner product term can be also expressed as matrix-vector multiplication:
    \begin{align}
      \left\langle \PDpflh, \PDpflhOld \right\rangle_{h}\PDpflhOld
        = \frac{1}{\left| e \right|^{2}}
            \begin{bmatrix}
              \left( *\pflhOld \right)^{2} & \pflhOld\left( *\pflhOld  \right) \\
              \pflhOld\left( *\pflhOld  \right) & \left( \pflhOld \right)^{2}
            \end{bmatrix} \cdot \PDpflh
        =: \left( \PDpflhOld \otimes_{h} \PDpflhOld \right)^{\sharp,\cdot} \cdot \PDpflh
    \end{align}
    with a formally defined local outer product \( \otimes_{h} \) for PD-1-forms,
    which respect the discrete local metric.

    With the Taylor linearization and the implicit Euler scheme, we have to solve in every time steps and all \( e\in\E \)
    \begin{align}
      \left[ \frac{1}{\tau} + K_{0}\LDRh + K_{n}\left( \left\| \PDpflhOld \right\|_{h}^{2} - 1 \right) \right]\PDpflh
          + 2K_{n} \left( \PDpflhOld \otimes_{h} \PDpflhOld \right) \cdot \PDpflh
          &= \left[\frac{1}{\tau} + 2K_{n}\left\| \PDpflhOld \right\|_{h}^{2}\right]\PDpflhOld
    \end{align}
    resp.
    %\resizebox{0.9\textwidth}{!}{\begin{minipage}{\linewidth}
    \begin{align} 
      \left[ \frac{1}{\tau}
          - \begin{bmatrix}
               K_{1} \\ K_{3}
            \end{bmatrix} \LCBh
            -\begin{bmatrix}
               K_{3} \\ K_{1}
            \end{bmatrix} \LBh
          + K_{n}\left( \left\| \PDpflhOld \right\|_{h}^{2} - 1 \right) \right]\PDpflh
          + 2K_{n} \left( \PDpflhOld \otimes_{h} \PDpflhOld \right) \cdot \PDpflh
          &= \left[\frac{1}{\tau} + 2K_{n}\left\| \PDpflhOld \right\|_{h}^{2}\right]\PDpflhOld
    \end{align}
    %\end{minipage}}
